Fast gravitational wave parameter estimation without compromises

### 2023-02-06 src/tex/ms.tex
Add Marylou's PNAS paper
Address Soichiro's comment

Since the computational cost of evaluating a waveform model scales linearly
with the number of time or frequency bins, the computational burden for
longer-duration signals is often quite large. To mitigate this, there are a
number of methods to reduce the number of basis points needed to compute the
likelihood faithfully \cite{Field:2011mf, Field:2013cfa, Smith:2016qas,
Vinciguerra:2017ngf}. In this work, we take advantage of likelihood
heterodyning \cite{Cornish:2021lje} (also known as relative binning
\cite{Zackay:2018qdy}).

@@

Note that every time we retrain the network, we are breaking the Markov
properties since we are changing the proposal distribution. To produce final
samples that can be used to estimate target quantities, one has to freeze the
normalizing flow model and not retrain during the final sampling phase in order
to satisfy the detailed balance condition. We use the package \textsc{flowMC}
\cite{2022arXiv221106397W}, with MALA as the gradient-based sampler. The
pseudocode of the algorithm is given in Algorithm \ref{alg:cap}.

>>>>

Since the computational cost of evaluating a waveform model scales linearly
with the number of time or frequency bins, the computational burden for
longer-duration signals is often quite large. To mitigate this, there are a
number of methods to reduce the number of basis points needed to compute the
likelihood faithfully \cite{Field:2011mf, Field:2013cfa, Smith:2016qas,
Vinciguerra:2017ngf,Morisaki:2020oqk,Morisaki:2021ngj}. In this work, we take advantage of likelihood
heterodyning \cite{Cornish:2021lje} (also known as relative binning
\cite{Zackay:2018qdy}).

@@

Note that every time we retrain the network, we are breaking the Markov
properties since we are changing the proposal distribution. To produce final
samples that can be used to estimate target quantities, one has to freeze the
normalizing flow model and not retrain during the final sampling phase in order
to satisfy the detailed balance condition. We use the package \textsc{flowMC}
\cite{2022arXiv221106397W,Gabrie:2021tlu}, with MALA as the gradient-based sampler. The
pseudocode of the algorithm is given in Algorithm \ref{alg:cap}.
